working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
more edits
changes
counts

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation. Therefore, 180 different combinations were performed with N=10 per combination. Seed set was the proxy of effect for all our treatments. Moreover, hand cross pollination (between individuals of the same species), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10). For the treatments with foreign pollen and hand cross pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Hand-pollination was conducted with 3-4 gentle touches on the stigma surface. For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed. Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.  In order to confirm that the treatments applied were the desire proportions, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).

@@

>>>>

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation. Therefore, 180 different combinations were performed with N=10 per combination. Seed set was the proxy of effect for all our treatments. Moreover, hand cross pollination (between individuals of the same species), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10). For the treatments with foreign pollen and hand cross pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Hand-pollination was conducted with 3-4 gentle touches on the stigma surface. For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed. Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.  In order to confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species calculated. In total 20 different heterospecific crosses were counted, all the focal species with crosses of just on species of the other two families (N=3).

@@

Add also plot with fruit production and pot it in appendix.Also the plots of ratios to appendices.

### 2019-02-26 Manuscript_draft/Manuscript_draft.tex
counts

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10) in order to see if foreign pollen
can trigger fruit production by itself or even seeds through ovule
usurpation. Therefore, 180 different combinations were performed with
N=10 per combination. Seed set was the proxy of effect for all our
treatments. Moreover, hand cross pollination (between individuals of the
same species), hand self pollination, apomixis (bagged emasculated
flowers) and natural selfing were tested for each species (N=10). For
the treatments with foreign pollen and hand cross pollination, flowers
were emasculated the day prior anthesis and hand pollinated next day
with a toothpick. Hand-pollination was conducted with 3-4 gentle touches
on the stigma surface. For each species 20 anthers were collected and
their pollen counted with a hemocytometer, each anther was counted 4
times and then an average of these counts was performed. Once, the
average number of pollen grains per anther was known, the proportion of
anthers per mix was calculated in order to achieve a 50-50\% mix. In
order to confirm that the treatments applied were the desire
proportions, for each focal species the total stigmatic load of pollen
was counted from one donor of each family (N=3).

@@

>>>>

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10) in order to see if foreign pollen
can trigger fruit production by itself or even seeds through ovule
usurpation. Therefore, 180 different combinations were performed with
N=10 per combination. Seed set was the proxy of effect for all our
treatments. Moreover, hand cross pollination (between individuals of the
same species), hand self pollination, apomixis (bagged emasculated
flowers) and natural selfing were tested for each species (N=10). For
the treatments with foreign pollen and hand cross pollination, flowers
were emasculated the day prior anthesis and hand pollinated next day
with a toothpick. Hand-pollination was conducted with 3-4 gentle touches
on the stigma surface. For each species 20 anthers were collected and
their pollen counted with a hemocytometer, each anther was counted 4
times and then an average of these counts was performed. Once, the
average number of pollen grains per anther was known, the proportion of
anthers per mix was calculated in order to achieve a 50-50\% mix. In
order to confirm that the treatments applied were the desire
proportions, for each focal species the total stigmatic load of pollen
was counted from one donor of each family (N=3). In order to test the
amount of pollen grains deposited on the stigma with heterospecific
pollinations we counted the total amount of pollen grains and we
calculated the proportions between the two species of the mix. We did
the counts for each species with crosses with one species of the other
two families, therefore 20 different types of mixes with 3 replicates.

@@

\href{Jose}{Add pollen on stigma counts to methods}

{[}Next bit to results, also divided it with {]}

Total pollen deposited on stigmas was significantly correlated with the
stigmatic area, pearsons correlation=0.57 and p-value=0.008. Proportions
of pollen talk about it to 50-50 mix? Talk aboout this in methods too.

Add also plot with fruit production and pot it in appendix.Also the
plots of ratios to appendices.
